\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[pdfauthor={George Kaplan},%
            pdftitle={George Kaplan's Resume},%
            pdfkeywords={Seriously, The, Best, Resume, Ever, Please, Hire, Me},%
            hidelinks,%
            bookmarks=false,%
            pdftoolbar=false,%
            pdfstartview={FitH}]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\voffset=0.2in
\renewcommand{\headrulewidth}{0pt}

\lhead{
  \Huge
  George Kaplan
}

\rhead{
  \footnotesize
  \href{mailto:kaplan.george@outlook.com}{kaplan.george@outlook.com} \\
  $518.852.4731$
}

\chead{
  \footnotesize
  Baltimore, MD \\
  \href{https://github.com/g-s-k}{github.com/g-s-k}
}

\lfoot{}
\cfoot{}
\rfoot{}

\newcommand{\dotfringe}{
    \begin{center}
      $\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots$
    \end{center}
}

\renewcommand{\labelitemi}{$\triangleright$}

\begin{document}
\pagenumbering{gobble}

\dotfringe{}

\section*{Education}
\subsection*{University of Maryland, College Park}
\textit{Bachelor's of Science in Physical Sciences} \hfill 2012 --- 2016
\begin{itemize}
  \item College Park Scholars: Science, Technology and Society
  \item Specialized coursework: Computing and Data Analysis, Applied Probability and Statistics, Radiochemistry, Structure Determination Using Spectroscopic Methods, Inorganic Chemistry, Geophysics, Observational Geophysics, Atmospheric Physics and Thermodynamics, Dynamics of the Atmosphere and Ocean
\end{itemize}

\dotfringe{}

\section*{Experience}
\subsection*{Nu-Tek Precision Optical Corporation}
\textit{Engineer} \hfill 2016 --- present
\begin{itemize}
  \item Developed and maintained a proprietary MATLAB toolbox for processing optical data.
  \item Automated administrative tasks with Python and PowerShell scripts.
  \item Created analytical and automation tools for manufacturing and metrology using C and Golang.
  \item Compiled, designed, and typeset product  certifications with \LaTeX{}.
  \item Implemented organization-wide code style standards and version control with Git.
  \item Created frontend web tools for monitoring orders and planning tasks.
  \item Tracked order progress and maintained detailed task records in Wrike (project management tool).
  \item Designed and optimized automated measurement programs using Zeiss CALYPSO.\@
\end{itemize}
\subsection*{The Research Foundation for SUNY}
\textit{Innovation and Partnerships Intern} \hfill Summer 2014 and 2015
\begin{itemize}
  \item Assisted in implementing the \href{https://startup.ny.gov/}{START-UP New York} and \href{https://www.rfsuny.org/Our-Work/Innovation-and-Partnerships/Programs/Technology-Accelerator-Fund/}{Technology Accelerator Fund} programs.
  \item Reviewed grant proposals to assess the feasibility and potential marketability of new technologies.
  \item Edited, compiled, and summarized legal documents for public distribution.
  \item Modelled the performance of a proposed venture capital fund using past financial data.
\end{itemize}
\subsection*{University of Maryland, College Park}
\textit{Teaching Assistant} \hfill 2014 --- 2015
\begin{itemize}
  \item Developed lesson plans and managed course logistics.
  \item Evaluated student performance and progress through weekly reflective writing assignments.
\end{itemize}
\dotfringe{}
\section*{Technical Skills}
\begin{itemize}
  \item MATLAB, Python 3, PowerShell, Golang, C/C\texttt{++}, Git, Bash, ES6, \LaTeX{}, REST APIs, Vim
  \item FreeCAD, Autodesk Inventor, Creo Parametric/Pro Engineer, Zeiss CALYPSO, ZYGO MetroPro/Mx
\end{itemize}

\dotfringe{}

\end{document}
