\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[pdfauthor={George Kaplan},%
            pdftitle={George Kaplan's Resume},%
            pdfkeywords={Seriously, The, Best, Resume, Ever, Please, Hire, Me},%
            hidelinks,%
            bookmarks=false,%
            pdftoolbar=false,%
            pdfstartview={FitH}]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\voffset=0.2in
\renewcommand{\headrulewidth}{0pt}
\lhead{\Huge George Kaplan}
\cfoot{}
\rhead{\footnotesize kaplan.george@outlook.com \\ $518.852.4731$}
\chead{\footnotesize Baltimore, MD \\ \href{https://github.com/g-s-k}{github.com/g-s-k}}
\lfoot{}
\rfoot{}

\newcommand{\dotfringe}{
    \begin{center}
      $\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots\cdots$
    \end{center}
}

\renewcommand{\labelitemi}{$\triangleright$}

\begin{document}
\pagenumbering{gobble}

\dotfringe{}

\section*{Education}
\subsection*{University of Maryland, College Park}
\textit{Bachelor's of Science in Physical Sciences} \hfill 2012 --- 2016
\begin{itemize}
  \item College Park Scholars: Science, Technology and Society
  \item Specialized coursework: Computing and Data Analysis, Applied Probability and Statistics, Radiochemistry, Structure Determination Using Spectroscopic Methods, Inorganic Chemistry, Geophysics, Observational Geophysics, Atmospheric Physics and Thermodynamics, Dynamics of the Atmosphere and Ocean
\end{itemize}

\dotfringe{}

\section*{Experience}
\subsection*{Nu-Tek Precision Optical Corporation}
\textit{Production Engineer} \hfill 2016 --- present
\begin{itemize}
  \item Developed and maintained proprietary MATLAB toolbox for processing optical data.
  \item Automated administrative tasks with Python and PowerShell scripts.
  \item Created analytical and automation tools for manufacturing and metrology using C and Golang.
  \item Compiled and typeset product quality certifications with \LaTeX.
  \item Tracked order progress and maintained detailed task records in our project management software.
  \item Collected in-process and final part data using a Zeiss CMM and CALYPSO software.
\end{itemize}
\subsection*{The Research Foundation for SUNY}
\textit{Innovation and Partnerships Intern} \hfill Summer 2014 and 2015
\begin{itemize}
  \item Assisted in implementing the \href{https://startup.ny.gov/}{START-UP New York} and \href{https://www.rfsuny.org/Our-Work/Innovation-and-Partnerships/Programs/Technology-Accelerator-Fund/}{Technology Accelerator Fund} programs.
  \item Managed databases in Access, assessed new technologies for marketability and reviewed grant proposals.
  \item Reviewed legal documents, corrected errors and inaccuracies, and prepared briefs for public distribution.
  \item Created a detailed financial model in Excel and projected ROI for a proposed venture capital fund.
\end{itemize}
\subsection*{University of Maryland, College Park}
\textit{Teaching Assistant} \hfill 2014 --- 2015
\begin{itemize}
  \item Developed lesson plans, accounted for instructional materials, and managed course logistics.
  \item Evaluated student performance and progress through weekly reflective writing assignments.
\end{itemize}
\dotfringe{}
\section*{Software \& Language Proficiency}
\begin{itemize}
  \item MATLAB, Python 3, PowerShell, Golang, C/C\texttt{++}, Bash, ES6, \LaTeX
  \item FreeCAD, Autodesk Inventor, Creo Parametric/Pro Engineer, Zeiss CALYPSO, ZYGO MetroPro/Mx
\end{itemize}

\dotfringe{}

\end{document}
