\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[pdfauthor={George Kaplan},%
            pdftitle={George Kaplan's Resume},%
            pdfkeywords={Seriously, The, Best, Resume, Ever, Please, Hire, Me},%
            hidelinks,%
            bookmarks=false,%
            pdftoolbar=false,%
            pdfstartview={FitH}]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\voffset=0.2in
\renewcommand{\headrulewidth}{0pt}

\lhead{\Huge George Kaplan}

\rhead{\footnotesize
\href{mailto:kaplan.george@outlook.com}{kaplan.george@outlook.com} \\
$+1.518.852.4731$ }

\chead{\footnotesize Baltimore, MD USA\\
\href{https://github.com/g-s-k}{github.com/g-s-k} }

\lfoot{}
\cfoot{}
\rfoot{}

\renewcommand{\labelitemi}{$\triangleright$}

\linespread{0.9}

\begin{document}
\pagenumbering{gobble}

\section*{Summary}
\paragraph{Programming Languages:} JavaScript / TypeScript, Rust, Elixir,
Golang, MATLAB, SCSS, \LaTeX\@

\paragraph{Frameworks \& Tools:} React, Phoenix, Serverless / AWS Lambda,
Docker, Kubernetes, Cargo, Make

\paragraph{Interests:} Music and audio technology, generative art, user
experience and accessibility, compilers

\dotfill

\section*{Experience}
\subsection*{Fearless Solutions}
\paragraph{}
\textit{Software Engineer 2} \hfill March 2021 --- present
\begin{itemize}
  \item Adopted and expanded a prototype application built with \textit{React}
    and the \textit{Serverless Framework} into a production-ready state, and
    delivered it to users on time. The improvements included support for data
    migration scripts, multiple new user types and workflows, and integration
    with legacy systems via \textit{Kafka}.
  \item Spearheaded an effort among technical personnel to improve code
    quality, test coverage, and user accessibility. This led to a significant
    decrease in defects and regressions pushed into our staging environment.
  \item Collaborated with security and operations teams to address findings
    from a pre-deployment audit. All findings were eliminated well in advance
    of the subsequent audit, and the deployment to production was able to
    proceed without incident.
\end{itemize}

\subsection*{Visionist Incorporated}
\paragraph{}
\textit{Engineer 3} \hfill November 2020 --- February 2021

\begin{itemize}
  \item Maintained and enhanced a group of analytics for audio data using
    Elixir as the API layer and Rust to implement the signal processing
    algorithms. These were integrated using the \textit{Rustler} library, and
    were chosen for Rust's performance characteristics and Elixir's robust
    operation in high-throughput systems.
  \item Fleshed out a system management interface from a minimal scaffold into
    a useful tool for systems administrators using the \textit{Phoenix
    LiveView} library.
\end{itemize}

\paragraph{}
\textit{Engineer 2} \hfill August 2018 --- October 2020

\begin{itemize}
  \item Helped scale a suite of applications for real-time geographic data
    analysis up from prototype to production, focusing on performance and
    reliability. Improved communication between the development team and our
    user base to implement a faster and more robust feedback loop.
  \item Built and maintained a richly interactive web form using \textit{React}
    to give users fine-grained control over their analytic rules. Incorporated
    usability recommendations from our UX specialists, feature requests from
    our users, and technical requirements from our contract in each iteration
    of the design.
\end{itemize}

\subsection*{Nu-Tek Precision Optical Corporation}
\paragraph{}
\textit{Engineer 1} \hfill May 2016 --- August 2018
\begin{itemize}
  \item Developed and maintained a proprietary MATLAB toolbox for processing a
    variety of optical data formats, supporting common manipulations such as
    Zernike decomposition, FFT analysis, and automated generation of corrective
    programs for computer-controlled polishing machines.
  \item Automated various administrative tasks such as printing work orders,
    tracking progress on each project, and generating customer documentation
    with \textit{PowerShell} and \LaTeX.
\end{itemize}

\dotfill

\section*{Education}
\subsection*{University of Maryland, College Park}
\paragraph{}
\textit{Bachelor's of Science in Physical Sciences} \hfill 2012 --- 2016

\begin{itemize}
  \item Concentrations in Atmospheric and Oceanic Science, Chemistry, and Geology
\end{itemize}

\end{document}
